
##Perform the transformation
```{r}
#Transform LandContour column
LC.lvl <- as.numeric(house$LandContour == 'Lvl')
LC.bnk <- as.numeric(house$LandContour == 'Bnk')
LC.hls <- as.numeric(house$LandContour == 'HLS')
LC.low <- as.numeric(house$LandContour == 'Low')

#Transform Utilities column
ut.allpub <- as.numeric(house$Utilities == 'AllPub')
ut.NoSeWa <- as.numeric(house$Utilities == 'NoSeWa')

#transform LotConfig
lotcon.inside <-as.numeric(house$LotConfig == 'Inside')
lotcon.corner <-as.numeric(house$LotConfig == 'Corner') 
lotcon.fr2 <- as.numeric(house$LotConfig == 'FR2')
lotcon.fr3 <-as.numeric(house$LotConfig == 'FR3')
lotcon.CulDSac<-as.numeric(house$LotConfig == 'CulDSac') 


#transform DwellClass
dwellclass.1Fam <- as.numeric(house$DwellClass == '1Fam') 
dwellclass.TwnhsE <- as.numeric(house$DwellClass == 'TwnhsE')
dwellclass.Duplex <- as.numeric(house$DwellClass == 'Duplex')

#transform garage type
garageType.2type <- ifelse(is.na(house$GarageType), 0, as.numeric(house$GarageType == '2Types'))
garageType.Attchd <- ifelse(is.na(house$GarageType), 0, as.numeric(house$GarageType == 'Attchd'))
garageType.Basment <- ifelse(is.na(house$GarageType), 0, as.numeric(house$GarageType == 'Basment'))
garageType.BuiltIn <- ifelse(is.na(house$GarageType), 0,as.numeric(house$GarageType == 'BuiltIn'))
garageType.CarPort <- ifelse(is.na(house$GarageType), 0,as.numeric(house$GarageType == 'CarPort'))
garageType.Detchd <- ifelse(is.na(house$GarageType), 0,as.numeric(house$GarageType == 'Detchd'))

#transfrom paved drive
pavedrive.paved <- as.numeric(house$PavedDrive == 'Y')
pavedrive.partial <- as.numeric(house$PavedDrive == 'P')
pavedrive.other <- as.numeric(house$PavedDrive == 'N')

#transform LotShape
lotshape.1 <- as.numeric(house$LotShape == 1)
lotshape.2 <- as.numeric(house$LotShape == 2)
lotshape.3 <- as.numeric(house$LotShape == 3)
lotshape.4 <- as.numeric(house$LotShape == 4)

#transform centralair
centralair <- ifelse(house$CentralAir == 'Y', 1, 0)

#transform Slope
slope <- case_when(
  house$Slope == 'Gtl' ~ 1,
  house$Slope == 'Mod' ~ 2,
  house$Slope == 'Sev' ~ 3,
  TRUE ~ NA_real_
)

#transform ExteriorCondition
exteriorcondition <- case_when(
  house$ExteriorCondition == 'Po' ~ 1,
  house$ExteriorCondition == 'Fa' ~ 2,
  house$ExteriorCondition == 'TA' ~ 3,
  house$ExteriorCondition == 'Gd' ~ 4,
  house$ExteriorCondition == 'Ex' ~ 5,
  TRUE ~ NA_real_
)

#transform BasementCondition
basementcondition <- case_when(
  house$BasementCondition == 'Po' ~ 1,
  house$BasementCondition == 'Fa' ~ 2,
  house$BasementCondition == 'TA' ~ 3,
  house$BasementCondition == 'Gd' ~ 4,
  house$BasementCondition == 'Ex' ~ 5,
  TRUE ~ 0
)
basementcondition.nobasement <- as.numeric(house$BasementCondition == 'NB')

sum(is.na(basementcondition.nobasement))

#transform KitchenQuality
kitchenquality <- case_when(
  house$KitchenQuality == 'Po' ~ 1,
  house$KitchenQuality == 'Fa' ~ 2,
  house$KitchenQuality == 'TA' ~ 3,
  house$KitchenQuality == 'Gd' ~ 4,
  house$KitchenQuality == 'Ex' ~ 5,
  TRUE ~ NA_real_
)

house_transform <- data.frame(LC.lvl, LC.bnk, LC.low, ut.allpub, ut.NoSeWa, lotcon.inside, lotcon.corner, lotcon.fr2, lotcon.fr3, lotcon.CulDSac, slope, dwellclass.1Fam, dwellclass.TwnhsE,dwellclass.Duplex, garageType.2type, garageType.Attchd, garageType.Basment, garageType.BuiltIn, garageType.CarPort, garageType.Detchd, pavedrive.paved, pavedrive.partial, pavedrive.other,lotshape.1,lotshape.2, lotshape.3, lotshape.4, exteriorcondition, basementcondition, basementcondition.nobasement, kitchenquality)



house_clean <- house %>%
  select(-LandContour, -Utilities, -LotConfig, -Slope, -DwellClass, -ExteriorCondition, -BasementCondition, -CentralAir, -KitchenQuality, -GarageType, -PavedDrive, -LotShape, -Id) %>%
  cbind(house_transform)
```
##Understanding the data
```{r}
#Calculate for continous variables
summary_mean <- house_clean %>% summarise(
  Lotarea = round(mean(LotArea, na.rm = TRUE),2),
  TotalBSF = round(mean(TotalBSF, na.rm = TRUE),2),
  LivingArea = round(mean(LivingArea, na.rm = TRUE),2),
  PoolArea = round(mean(PoolArea, na.rm = TRUE),2),
  OpenPorchSF = round(mean(OpenPorchSF, na.rm = TRUE),2),
  LowQualFinSF = round(mean(LowQualFinSF, na.rm = TRUE),2),
  SalePrice = round(mean(SalePrice, na.rm = TRUE),2))

summary_max <- house_clean %>% summarise(
  Lotarea = round(max(LotArea, na.rm = TRUE),2),
  TotalBSF = round(max(TotalBSF, na.rm = TRUE),2),
  LivingArea = round(max(LivingArea, na.rm = TRUE),2),
  PoolArea = round(max(PoolArea, na.rm = TRUE),2),
  OpenPorchSF = round(max(OpenPorchSF, na.rm = TRUE),2),
  LowQualFinSF = round(max(LowQualFinSF, na.rm = TRUE),2),
  SalePrice = round(max(SalePrice, na.rm = TRUE),2))

summary_min <- house_clean %>% summarise(
  Lotarea = round(min(LotArea, na.rm = TRUE),2),
  TotalBSF = round(min(TotalBSF, na.rm = TRUE),2),
  LivingArea = round(min(LivingArea, na.rm = TRUE),2),
  PoolArea = round(min(PoolArea, na.rm = TRUE),2),
  OpenPorchSF = round(min(OpenPorchSF, na.rm = TRUE),2),
  LowQualFinSF = round(min(LowQualFinSF, na.rm = TRUE),2),
  SalePrice = round(min(SalePrice, na.rm = TRUE),2))

summary_median <- house_clean %>% summarise(
  Lotarea = round(median(LotArea, na.rm = TRUE),2),
  TotalBSF = round(median(TotalBSF, na.rm = TRUE),2),
  LivingArea = round(median(LivingArea, na.rm = TRUE),2),
  PoolArea = round(median(PoolArea, na.rm = TRUE),2),
  OpenPorchSF = round(median(OpenPorchSF, na.rm = TRUE),2),
  LowQualFinSF = round(median(LowQualFinSF, na.rm = TRUE),2),
  SalePrice = round(median(SalePrice, na.rm = TRUE),2))

summary_sd <- house_clean %>% summarise(
  Lotarea = round(sd(LotArea, na.rm = TRUE),2),
  TotalBSF = round(sd(TotalBSF, na.rm = TRUE),2),
  LivingArea = round(sd(LivingArea, na.rm = TRUE),2),
  PoolArea = round(sd(PoolArea, na.rm = TRUE),2),
  OpenPorchSF = round(sd(OpenPorchSF, na.rm = TRUE),2),
  LowQualFinSF = round(sd(LowQualFinSF, na.rm = TRUE),2),
  SalePrice = round(sd(SalePrice, na.rm = TRUE),2))

measurement <- c('mean', 'max', 'min', 'median','sd')

summary_continous <- rbind(summary_mean, summary_max,summary_min, summary_median,summary_sd )

summary_continous <- cbind(measurement,summary_continous)
View(summary_continous)

##Count for nominal variable 
summary_nominal_count <- house_transform %>% select(-exteriorcondition, -basementcondition, -kitchenquality, -slope ) %>%
  colSums(na.rm = TRUE)
summary_nominal_count

##Count for ordinal variable
exteriorcondition <- table(house_clean$exteriorcondition)
basementcondition <- table(house_clean$basementcondition)
kitchenquality <- table(house_clean$kitchenquality)
slope <- table(house_clean$slope)
OverallQuality <- table(house_clean$OverallQuality)
OverallCondition <- table(house_clean$OverallCondition)
MoSold <- table(house_clean$MoSold)

print('exteriorcondition')
exteriorcondition

print('basementcondition')
basementcondition

print('kitchenquality')
kitchenquality

print('slope')
slope

print('OverallQuality')
OverallQuality

print('OverallCondition')
OverallCondition

print('MoSold')
MoSold
```

##Data distribution
```{r}
#Draw histogram
png("Q3_histogram.png", width = 800, height = 600)

par(mfrow = c(2,4), mar = c(2, 2, 1, 1))
hist(house_clean$LotArea, col= '#BEDC74', main = 'Lot Area', xlab = '')
hist(house_clean$TotalBSF, col= '#BEDC74', main = 'Total BSF', xlab = '')
hist(house_clean$LivingArea, col= '#BEDC74', main = 'Living Area', xlab = '')
hist(house_clean$PoolArea, col= '#BEDC74', main = 'Pool Area', xlab = '')
hist(house_clean$OpenPorchSF, col= '#BEDC74', main = 'Open Porch SF', xlab = '')
hist(house_clean$LowQualFinSF, col= '#BEDC74', main = 'Low Qual Fin SF', xlab = '')
hist(house_clean$SalePrice, col= '#BEDC74', main = 'Sale Price', xlab = '')


dev.off()


#Summary statistic
continous <- house_clean %>% select('LotArea', 'TotalBSF', 'LivingArea', 'PoolArea', 'OpenPorchSF','LowQualFinSF', 'SalePrice')

summary(continous)

View(continous)

#CV calculation
summary_cv <- summary_sd/summary_mean
View(summary_cv)

```

##Missing values
```{r}
#Identify missing values
png("Q4_missingnessmap.png", width = 800, height = 600)
missmap(house_clean, col=c('red','#BEDC74'),y.at= 1,y.labels='',legend=TRUE)
dev.off()

which(colSums(is.na(house_clean)) > 0)

#Replace missing values with 0
house_zero <- house_clean
house_zero[is.na(house_zero)] <- 0


#replace with mean
house_mean <- house_clean

house_mean$LivingArea[is.na(house_mean$LivingArea)] <- mean(house_mean$LivingArea, na.rm = TRUE)
house_mean$YearBuilt[is.na(house_mean$YearBuilt)] <- mean(house_mean$YearBuilt, na.rm = TRUE)


#Compare house_zero and house_mean with original

png("Q4_livingarea.png", width = 800, height = 600)

plot(density(house_clean$LivingArea, na.rm = TRUE), col = 'red', main = 'Living area original (Red) vs Transformed\nvia replacing with 0(violet) and with mean(green)')
lines(density(house_mean$LivingArea), col = 'green')
lines(density(house_zero$LivingArea), col = 'violet')
dev.off()

png("Q4_Yearbuilt.png", width = 800, height = 600)
plot(density(house_clean$YearBuilt, na.rm = TRUE), col = 'red', main = 'Year built original (Red) vs Transformed\nvia replacing with 0(violet) and with mean(green)')
lines(density(house_mean$YearBuilt), col = 'green')
lines(density(house_zero$YearBuilt), col = 'violet')
dev.off()

#delete missing values
house_delete <- house_clean[complete.cases(house_clean), ]

png("Q4_saleprice.png", width = 800, height = 600)
plot(density(house_clean$SalePrice, na.rm = TRUE), col = 'red', main = 'Sales price original (Red) vs Transformed\nvia  deleting NA (blue)')
lines(density(house_delete$SalePrice), col = 'blue')

png("Q4_livingarea_delete.png", width = 800, height = 600)
plot(density(house_clean$LivingArea, na.rm = TRUE), col = 'red', main = 'Living area original (Red) vs Transformed\nvia  deleting NA (blue)')
lines(density(house_delete$LivingArea), col = 'blue')

png("Q4_yearbuilt_delete.png", width = 800, height = 600)
plot(density(house_clean$YearBuilt, na.rm = TRUE), col = 'red', main = 'Year build original (Red) vs Transformed\nvia  deleting NA (blue)')
lines(density(house_delete$YearBuilt), col = 'blue')

dev.off()
```


##Dimension Reduction
```{r}
#Subset target variables

house_variables <- subset(house_delete, select = -SalePrice)
target <- house_delete$SalePrice

#Visualize the correlation
cor_matrix <- cor(house_variables)

png("Q5_correlation.png", width = 800, height = 600)
corrplot(cor_matrix, method = "color", tl.cex = 0.5)
dev.off()

#Identify variables with high correlation coefficient
M <- data.matrix(house_variables)
corrM <- cor(M)

highlyCorrM <- findCorrelation(corrM, cutoff=0.5)
names(house_variables)[highlyCorrM]

#check variance of potential candidates for dimension reduction
table(house_variables$slope)
table(house_variables$lotcon.inside)
table(house_variables$LC.lvl)

#Proceed with dimension reduction

house_reduce <- subset(house_variables, select = -c(ut.NoSeWa, TotalRmsAbvGrd))
table(house_variables$PoolArea)
```

##Input variables distribution against SalePrice
```{r}
#Distribution of continous variables against SalePrice

png("Q5_continousdistribution.png", width = 800, height = 600)
continous_distribution <- house_delete %>% select('LotArea', 'TotalBSF', 'LivingArea', 'PoolArea', 'OpenPorchSF', 'SalePrice', 'YearBuilt', 'LowQualFinSF')
continous_distribution_plot <- continous_distribution %>%
  keep(is.numeric) %>% 
  gather(key = "Variable", value = "Value", -SalePrice) %>%
  ggplot(aes(x = Value, y = SalePrice)) +  # Plot Value against Sale_Price
  facet_wrap(~ Variable, scales = "free") + # Create facets for each variable
  geom_point(color = '#BEDC74', alpha = 0.5) +                # Scatter plot with some transparency
  theme_minimal() +                        # Clean theme
  labs(x = "Variable Value", y = "Sale Price", 
       title = "Scatter Plots of Continous variable vs Sale Price")
continous_distribution_plot
dev.off()

#Distribution of discrete variables against SalePrice
png("Q5_discretedistribution.png", width = 800, height = 600)
discrete_distribution <- house_delete %>% select('FullBath', 'HalfBath', 'TotalRmsAbvGrd', 'BedroomAbvGr', 'KitchenAbvGr', 'Fireplaces', 'GarageCars', 'YrSold','SalePrice')
discrete_distribution_plot <- discrete_distribution %>%
  keep(is.numeric) %>% 
  gather(key = "Variable", value = "Value", -SalePrice) %>%
  ggplot(aes(x = Value, y = SalePrice)) +  
  facet_wrap(~ Variable, scales = "free") + 
  geom_jitter(color = '#BEDC74', width = 0.1, height = 0) +     
  theme_minimal() +                      
  labs(x = "Variable Value", y = "Sale Price", 
       title = "Jitter plot of Discrete Variables vs Sale Price")
discrete_distribution_plot
dev.off()

#Distribution of Nominal variables against SalePrice
png("Q5_nominal1.png", width = 800, height = 600)
common_columns <- intersect(names(house_delete), names(summary_nominal_count))
nominal_distribution <- house_delete %>% select(all_of(common_columns),SalePrice )
nominal_distribution_plot1 <- nominal_distribution %>%
  select(1:9,SalePrice ) %>%
  keep(is.numeric) %>% 
  gather(key = "Variable", value = "Value", -SalePrice) %>%
  filter(Value == 1) %>%
  ggplot(aes(x = as.factor(Value), y = SalePrice)) +  
  facet_wrap(~ Variable, scales = "free") + 
  geom_boxplot(fill = '#BEDC74') +     
  theme_minimal() +                      
  labs(x = "Variable Value", y = "Sale Price", 
       title = "Boxplots of Categorical Variables vs Sale Price")
nominal_distribution_plot1
dev.off()

png("Q5_nominal2.png", width = 800, height = 600)
nominal_distribution_plot2 <- nominal_distribution %>%
  select(10:18,SalePrice ) %>%
  keep(is.numeric) %>% 
  gather(key = "Variable", value = "Value", -SalePrice) %>%
  filter(Value == 1) %>%
  ggplot(aes(x = as.factor(Value), y = SalePrice)) +  
  facet_wrap(~ Variable, scales = "free") + 
  geom_boxplot(fill = '#BEDC74') +     
  theme_minimal() +                      
  labs(x = "Variable Value", y = "Sale Price", 
       title = "Boxplots of Categorical Variables vs Sale Price")
nominal_distribution_plot2
dev.off()

png("Q5_nominal3.png", width = 800, height = 600)
nominal_distribution_plot3 <- nominal_distribution %>%
  select(19:28,SalePrice ) %>%
  keep(is.numeric) %>% 
  gather(key = "Variable", value = "Value", -SalePrice) %>%
  filter(Value == 1) %>%
  ggplot(aes(x = as.factor(Value), y = SalePrice)) +  
  facet_wrap(~ Variable, scales = "free") + 
  geom_boxplot(fill = '#BEDC74') +     
  theme_minimal() +                      
  labs(x = "Variable Value", y = "Sale Price", 
       title = "Boxplots of Categorical Variables vs Sale Price")
nominal_distribution_plot3
dev.off()

#Distribution of ordinal variable against SalePrice
png("Q5_ordinal.png", width = 800, height = 600)
ordinal_distribution <- house_delete %>% select('OverallQuality', 'OverallCondition', 'exteriorcondition', 'basementcondition', 'kitchenquality', 'slope', 'MoSold', 'SalePrice' )
ordinal_distribution_plot <- ordinal_distribution %>%
  keep(is.numeric) %>% 
  gather(key = "Variable", value = "Value", -SalePrice) %>%
  ggplot(aes(x = as.factor(Value), y = SalePrice)) +  
  facet_wrap(~ Variable, scales = "free") + 
  geom_boxplot(fill  = '#BEDC74') +     
  theme_minimal() +                      
  labs(x = "Variable Value", y = "Sale Price", 
       title = "Boxplots of Categorical Variables vs Sale Price")
ordinal_distribution_plot
dev.off()


```


##Regression Modelling 
```{r}

#Merge target variable back to dataset
house_reduce$SalePrice <- target

# Assign formula
formula = SalePrice  ~.


#Data partition 
smp_size <- floor(2/3 * nrow(house_reduce)) 

set.seed(2)
house_reduce_1 <- house_reduce[sample(nrow(house_reduce)), ]


house1.train <- house_reduce_1[1:smp_size, ] 
house1.test <- house_reduce_1[(smp_size+1):nrow(house_reduce_1), ]


```

###Data 1
```{r}
#Create model parameters
model_1 <- lm(formula = formula, data = house1.train)

#Forming formula
formula_1 <- as.formula(
 paste0("y ~ ", round(coefficients(model_1)[1],2), " + ", 
 paste(sprintf("%.2f * %s",coefficients(model_1)[-1],
 names(coefficients(model_1)[-1])), 
 collapse=" + ")
 )
)

formula_1

summary(model_1)

#Evaluate the model
house1.train$predicted.saleprice <- predict(model_1, house1.train)
house1.test$predicted.saleprice <- predict(model_1, house1.test)

pl1 <-house1.test %>%
 ggplot(aes(SalePrice,predicted.saleprice)) +
 geom_point(alpha=0.5) +
 stat_smooth(aes(colour='red')) +
 xlab('Actual value') +
 ylab('Predicted value')+
 ggtitle('Regression modelling 1')
 theme_bw()
ggplotly(pl1)

r_squared_1 <- summary(model_1)$r.squared

error_1 <- house1.test$SalePrice-house1.test$predicted.saleprice
rmse_1 <- sqrt(mean(error_1^2))

round(r_squared_1,2)
rmse_1

dataset1 <- c(round(r_squared_1,2), round(rmse_1,2))

table(house_reduce$lotcon.CulDSac)
```

###Data 2
```{r}
house_reduce_2 <- subset(house_reduce_1, select= -c(ut.allpub,lotcon.inside, pavedrive.paved, lotshape.4))


house2.train <- house_reduce_2[1:smp_size, ] 
house2.test <- house_reduce_2[(smp_size+1):nrow(house_reduce_2), ]

model_2 <- lm(formula = formula, data = house2.train)

formula_2 <- as.formula(
 paste0("y ~ ", round(coefficients(model_2)[1],2), " + ", 
 paste(sprintf("%.2f * %s",coefficients(model_2)[-1],
 names(coefficients(model_2)[-1])), 
 collapse=" + ")
 )
)

formula_2

summary(model_2)

house2.train$predicted.saleprice <- predict(model_2, house2.train)
house2.test$predicted.saleprice <- predict(model_2, house2.test)

pl2 <-house2.test %>%
 ggplot(aes(SalePrice,predicted.saleprice)) +
 geom_point(alpha=0.5) +
 stat_smooth(aes(colour='red')) +
 xlab('Actual value') +
 ylab('Predicted value')+
 ggtitle('Regression modelling 2')+
 theme_bw()
ggplotly(pl2)

r_squared_2 <- summary(model_2)$r.squared

error_2 <- house2.test$SalePrice-house2.test$predicted.saleprice
rmse_2 <- sqrt(mean(error_2^2))

r_squared_2
rmse_2

dataset2 <- c(round(r_squared_2,2), round(rmse_2,2))
```

###Data 3
```{r}
house_reduce_3 = subset(house_reduce_1, select= -c(ut.allpub, lotcon.inside, pavedrive.paved, lotshape.4, lotcon.CulDSac, pavedrive.other))
house_reduce_3


house3.train <- house_reduce_3[1:smp_size, ] 
house3.test <- house_reduce_3[(smp_size+1):nrow(house_reduce_3), ]

model_3 <- lm(formula = formula, data = house3.train)

formula_3 <- as.formula(
 paste0("y ~ ", round(coefficients(model_3)[1],2), " + ", 
 paste(sprintf("%.2f * %s",coefficients(model_3)[-1],
 names(coefficients(model_3)[-1])), 
 collapse=" + ")
 )
)
formula_3

summary(model_3)

house3.train$predicted.saleprice <- predict(model_3, house3.train)
house3.test$predicted.saleprice <- predict(model_3, house3.test)

pl3 <-house3.test %>%
 ggplot(aes(SalePrice,predicted.saleprice)) +
 geom_point(alpha=0.5) +
 stat_smooth(aes(colour='red')) +
 xlab('Actual value') +
 ylab('Predicted value')+
 ggtitle('Regression modelling 3')
 theme_bw()
ggplotly(pl3)

r_squared_3 <- summary(model_3)$r.squared

error_3 <- house3.test$SalePrice-house3.test$predicted.saleprice
rmse_3 <- sqrt(mean(error_3^2))

r_squared_3
rmse_3

dataset3 <- c(round(r_squared_3,2), round(rmse_3,2))
```
###Data 4
```{r}
house_reduce_4 = subset(house_reduce_1, select= -c(ut.allpub, lotcon.inside, pavedrive.paved, lotshape.4, lotcon.CulDSac, pavedrive.other, LC.lvl))


house4.train <- house_reduce_4[1:smp_size, ] 
house4.test <- house_reduce_4[(smp_size+1):nrow(house_reduce_4), ]

model_4 <- lm(formula = formula, data = house4.train)

summary(model_4)

house4.train$predicted.saleprice <- predict(model_4, house4.train)
house4.test$predicted.saleprice <- predict(model_4, house4.test)

pl4 <-house4.test %>%
 ggplot(aes(SalePrice,predicted.saleprice)) +
 geom_point(alpha=0.5) +
 stat_smooth(aes(colour='red')) +
 xlab('Actual value') +
 ylab('Predicted value')+
 ggtitle('Regression modelling 4')
 theme_bw()
ggplotly(pl4)

r_squared_4 <- summary(model_4)$r.squared

metrics_4 <- postResample(pred = house4.test$predicted.saleprice, obs = house4.test$SalePrice)
metrics_4

error_4 <- house4.test$SalePrice-house4.test$predicted.saleprice
rmse_4 <- sqrt(mean(error_4^2))

r_squared_4
rmse_4

dataset4 <- c(round(r_squared_4,2), round(rmse_4,2))
```


###table of evaluation metrics 
```{r}
metric_name <- c('R_squared', 'RMSE')

metric_table <- rbind(metric_name, dataset1, dataset2, dataset3, dataset4)
View(metric_table)

```

##Decision tree
###Initial decision tree
```{r}
#Data configuration
smp_size.dt <- floor((2/3) *nrow(house_clean))

set.seed(3)
house.dt <- house_clean[sample(nrow(house_clean)), ]

house.dt$SalePrice <- house.dt$SalePrice/1000

#Create test and train dataset
house.dt_train <- house.dt[1:smp_size.dt, ]
house.dt_test <- house.dt[(smp_size.dt+1): nrow(house.dt), ]

#Set target and input variable
formula_dt = SalePrice~.

#Build and visualize decision tree
dtree <- rpart(formula_dt, data=house.dt_train, method="anova")

dtree$variable.importance

png("PartC_Decisiontree_initial.png", width = 800, height = 600)
rpart.plot(dtree, type = 4, fallen.leaves = FALSE, main = "Initial decision tree")
dev.off()

summary(dtree)

predicted.saleprice.dt <- predict(dtree, house.dt_test)

r_squred.dt <- postResample(pred = predicted.saleprice.dt*1000, obs = house.dt_test$SalePrice*1000)

error.dt <- (house.dt_test$SalePrice - predicted.saleprice.dt)*1000
rmse.dt <- sqrt(mean(error.dt^2))
rmse.dt
r_squred.dt

```

###Decision with best CP value
```{r}
printcp(dtree)
dtree$cptable[which.min(dtree$cptable[,"xerror"]),"CP"]

pruned_dtree <- prune(dtree, cp = 0.01) 

png("PartC_Decisiontree_bestCP.png", width = 800, height = 600)
rpart.plot(pruned_dtree, type = 4, fallen.leaves = FALSE, main = "Decision tree with CP =0.01 (Best CP)")
dev.off()

predicted.saleprice.prunned_dt <- predict(pruned_dtree, house.dt_test)

r_squred.prunned<- postResample(pred = predicted.saleprice.prunned_dt*1000, obs = house.dt_test$SalePrice*1000)
r_squred.prunned

error_prunned <- (house.dt_test$SalePrice - predicted.saleprice.prunned_dt)*1000
rmse.prunned <- sqrt(mean(error_prunned^2))

rmse.prunned
```

###Decision tree with increased CP value
```{r}
dtree_3 <- prune(dtree, cp = 0.02) 

png("PartC_Decisiontree_increaseCP.png", width = 800, height = 600)
rpart.plot(dtree_3, type = 4, fallen.leaves = FALSE, main = "Decision tree with CP =0.02")
dev.off()

predicted.saleprice.dt_3 <- predict(dtree_3, house.dt_test)

r_squred.prunned_3<- postResample(pred = predicted.saleprice.dt_3*1000, obs = house.dt_test$SalePrice*1000)
r_squred.prunned_3

error_prunned_3 <- (house.dt_test$SalePrice - predicted.saleprice.dt_3)*1000
rmse.prunned_3 <- sqrt(mean(error_prunned_3^2))

rmse.prunned_3
```

###Decision tree with decreased CP value
```{r}
dtree_4 <- prune(dtree, cp = 0.001) 

png("PartC_Decisiontree_decreseCP.png", width = 800, height = 600)
rpart.plot(dtree_4, type = 4, fallen.leaves = FALSE, main = "Decision tree with CP =0.001")
dev.off()

predicted.saleprice.dt_4 <- predict(dtree_4, house.dt_test)
summary(dtree_4)

r_squred.prunned_4<- postResample(pred = predicted.saleprice.dt_4*1000, obs = house.dt_test$SalePrice*1000)
r_squred.prunned_4

error_prunned_4 <- house.dt_test$SalePrice - predicted.saleprice.dt_4
rmse.prunned_4 <- sqrt(mean(error_prunned_4^2))

rmse.prunned_4
```

###Table of evaluation metrics
```{r}
rmse_decisiontree <- c(rmse.dt,rmse.prunned,rmse.prunned_3,rmse.prunned_4)
Decision_tree <- c('Original', 'CP = 0.01', 'CP=0.02', 'CP = 0.001')

evaluation_metrics <- rbind(Decision_tree,rmse_decisiontree )

View(evaluation_metrics)
